Is structure based drug design ready for selectivity optimization?

### 2018-12-14 manuscript.tex
checking in new figures and captions

\begin{figure}
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/figure3.png}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:figure-3}
{\bf CDK2 and ERK2 selectivity dataset from Blake et \emph{al}., 2016} \\
({\bf A})  \emph{(top)} Crystal structure of CDK2 (5K4J) shown in gray cartoon and ligand 22 shown in yellow spheres. \emph{(bot)} 2D interaction map of ligand 22 in the binding pocket of CDK2
({\bf B}) \emph{(top)} Crystal structure of ERK2 (5K4I) shown in gray cartoon with ligand 22 shown in yellow spheres. \emph{(bot)} 2D interaction map of ligand 22 in the binding pocket of ERK2.
({\bf C}) \emph{(top)} Common scaffold for all of the ligands in the Blake dataset, with R denoting attachment side for substitutions. \emph{(bot)} Table showing R group substitutions and experimentally measured binding affinities and selectivities. Ligand numbers correspond to those used in publication. 
}
\end{fullwidth}
\end{figure}

@@

\begin{figure}
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/figure4.png}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:figure-4}
{\bf Relative free energy calculations can accurately predict potency, but show larger errors for selectivity predictions.} \\
Single target potencies and selectivities for CDK2/ERK2 from the Blake datasets (\emph{top}), and CDK2/CDK9 (\emph{bottom}) from the Shao datasets. The experimental values are shown on the X-axis and calculated values on the Y-axis. Each data point corresponds to a ligand for a given target. All values are shown in units of kcal/mol. The horizontal error bars show the assumed experimental uncertainty of 0.3 kcal/mol\citep{BROWN2009420}. To better highlight outliers that are unlikely due simply to forcefield errors, we presume the forcefield error ($\sigma_\mathrm{FF} \approx$ 0.9 kcal mol$^{-1}$~\cite{Harder:J.Chem.TheoryComput.:2016}) also behaves as a random error. We show the total estimated statistical and forcefield error ($\sqrt{\sigma_\mathrm{FF}^2 + \sigma_\mathrm{calc}^2}$) as vertical blue error bars. The black vertical error bars correspond to the statistical error ($\sigma_{calc}$). The black line indicates agreement between calculation and experiment, while the gray shaded region represent 1.36 kcal/mol (or 1 log unit) error. The MUE and RMSE are shown on each plot with bootstrapped 95$\%$ confidence intervals.
}
\end{fullwidth}
\end{figure}

@@

\begin{figure}
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/figure5.png}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:figure-5}
{\bf Correlation in selectivity prediction errors can be used to accelerate selectivity optimization} \\
({\bf A}) (\emph{left}) The joint posterior distribution of the prediction errors for CDK2 (X-axis) and ERK2 (Y-axis) from the Bayesian graphical model. (\emph{right}) Speedup in selectivity optimization (Y-axis) as a function of correlation coefficient (X-axis). The posterior marginal distribution of the correlation coefficient ($\rho$) is shown in gray, while the expected speed up is shown for 100x (green curve) and 10x (yellow curve) selectivity optimization. The inserted box shows the mean and 95\% confidence interval for the correlation coefficient. 
({\bf B}) (\emph{left}) The same as above, with CDK2 (X-axis) and CDK9 (Y-axis). (\emph{right}) As above, for the CDK2/CDK9 calculations.}
\end{fullwidth}
\end{figure}

@@

\begin{figure}[h]
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/supp_figure4.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:sup-figure-4}
{\bf Each replicate of the CDK2/CDK9 calculates yields a consistent RMSE and MUE} \\
Single target potencies and selectivities for CDK2/ERK2 from the Blake datasets (\emph{top}), and CDK2/CDK9 (\emph{bottom}) from the Shao datasets. The experimental values are shown on the X-axis and calculated values on the Y-axis. Each data point corresponds to a ligand for a given target. All values are shown in units of kcal/mol. The horizontal error bars show the assumed experimental uncertainty of 0.3 kcal/mol\citep{BROWN2009420}. To better highlight outliers that are unlikely due simply to forcefield errors, we presume the forcefield error ($\sigma_\mathrm{FF} \approx$ 0.9 kcal mol$^{-1}$~\cite{Harder:J.Chem.TheoryComput.:2016}) also behaves as a random error. We show the total estimated statistical and forcefield error ($\sqrt{\sigma_\mathrm{FF}^2 + \sigma_\mathrm{calc}^2}$) as vertical blue error bars. The black vertical error bars correspond to the statistical error ($\sigma_{calc}$). The black line indicates agreement between calculation and experiment, while the gray shaded region represent 1.36 kcal/mol (or 1 log unit) error. The MUE and RMSE are shown on each plot with bootstrapped 95$\%$ confidence intervals. ({\bf A}) Replcicate 1 ({\bf B}) Replcicate 2 ({\bf C}) Replcicate 3 
}
\end{fullwidth}
\end{figure}

\begin{figure}[h]
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/supp_figure5.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:sup-figure-5}
{\bf Each replicate of the CDK2/CDK9 calculates yields consistent errors and correlation coefficient} \\
({\bf A}) (\emph{left}) The joint posterior distribution of the prediction errors for CDK2 (X-axis) and CDK9 (Y-axis) from the Bayesian graphical model for replicate 1. (\emph{right}) The posterior marginal distribution of the correlation coefficient ($\rho$) is shown in gray for replcicate 1. The inserted box shows the mean and 95\% confidence interval for the correlation coefficient. ({\bf B}) and ({\bf C}) The same as above, but for replicates 2 and 3, respectively
}
\end{fullwidth}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{figure}
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/figure3.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:figure-3}
{\bf CDK2 and ERK2 selectivity dataset from Blake et \emph{al}., 2016} \\
({\bf A})  \emph{(top)} Crystal structure of CDK2 (5K4J) shown in gray cartoon and ligand 22 shown in yellow spheres. \emph{(bot)} 2D interaction map of ligand 22 in the binding pocket of CDK2
({\bf B}) \emph{(top)} Crystal structure of ERK2 (5K4I) shown in gray cartoon with ligand 22 shown in yellow spheres. \emph{(bot)} 2D interaction map of ligand 22 in the binding pocket of ERK2.
({\bf C}) \emph{(top)} Common scaffold for all of the ligands in the Blake dataset, with R denoting attachment side for substitutions. \emph{(bot)} Table showing R group substitutions and experimentally measured binding affinities and selectivities. Ligand numbers correspond to those used in publication. 
}
\end{fullwidth}
\end{figure}

@@

\begin{figure}
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/figure4.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:figure-4}
{\bf Relative free energy calculations can accurately predict potency, but show larger errors for selectivity predictions.} \\
Single target potencies and selectivities for CDK2/ERK2 from the Blake datasets (\emph{top}), and CDK2/CDK9 (\emph{bottom}) from the Shao datasets. The experimental values are shown on the X-axis and calculated values on the Y-axis. Each data point corresponds to a ligand for a given target. All values are shown in units of kcal/mol. The horizontal error bars show the assumed experimental uncertainty of 0.3 kcal/mol\citep{BROWN2009420}. We show the 95\% CI based on the estimated statistical ($\sigma_{stat}$) as vertical blue error bars. For selectivity, the errors were propagated under the assumption that they were completely uncorrelated. The black line indicates agreement between calculation and experiment, while the gray shaded region represent 1.36 kcal/mol (or 1 log unit) error. The MUE and RMSE are shown on each plot with bootstrapped 95$\%$ confidence intervals.
}

\end{fullwidth}
\end{figure}

@@

\begin{figure}
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/figure5.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:figure-5}
{\bf Correlation in selectivity prediction errors can be used to accelerate selectivity optimization} \\
({\bf A}) (\emph{left}) The joint posterior distribution of the prediction errors for CDK2 (X-axis) and ERK2 (Y-axis) from the Bayesian graphical model. (\emph{right}) Speedup in selectivity optimization (Y-axis) as a function of correlation coefficient (X-axis). The posterior marginal distribution of the correlation coefficient ($\rho$) is shown in gray, while the expected speed up is shown for 100x (green curve) and 10x (yellow curve) selectivity optimization. The inserted box shows the mean and 95\% confidence interval for the correlation coefficient. 
({\bf B}) (\emph{left}) The same as above, with CDK2 (X-axis) and CDK9 (Y-axis). (\emph{right}) As above, for the CDK2/CDK9 calculations.}
\end{fullwidth}
\end{figure}

@@

\begin{figure}[h]
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/supp_figure4.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:sup-figure-4}
{\bf Each replicate of the CDK2/CDK9 calculations yields a consistent RMSE and MUE} \\
Three replicates of the CDK2/CDK9 calculations with different random seeds, but otherwise the same input structures, files, and parameters. The experimental values are shown on the X-axis and calculated values on the Y-axis. Each data point corresponds to a ligand for a given target. All values are shown in units of kcal/mol. The horizontal error bars show the assumed experimental uncertainty of 0.3 kcal/mol\citep{BROWN2009420}.We show the 95\% CI based on the estimated statistical as vertical blue error bars. For selectivity, the errors were propagated under the assumption that they were completely uncorrelated. The black line indicates agreement between calculation and experiment, while the gray shaded region represent 1.36 kcal/mol (or 1 log unit) error. The MUE and RMSE are shown on each plot with bootstrapped 95$\%$ confidence intervals. ({\bf A}) Replicate 1 ({\bf B}) Replicate 2 ({\bf C}) Replicate 3}

\end{fullwidth}
\end{figure}

\begin{figure}[h]
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/supp_figure5.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:sup-figure-5}
{\bf Each replicate of the CDK2/CDK9 calculations yields consistent errors and correlation coefficient} \\
({\bf A}) (\emph{left}) The joint posterior distribution of the prediction errors for CDK2 (X-axis) and CDK9 (Y-axis) from the Bayesian graphical model for replicate 1. (\emph{right}) The posterior marginal distribution of the correlation coefficient ($\rho$) is shown in gray for replcicate 1. The inserted box shows the mean and 95\% confidence interval for the correlation coefficient. ({\bf B}) and ({\bf C}) The same as above, but for replicates 2 and 3, respectively
}
\end{fullwidth}
\end{figure}

\begin{figure}[h]
	\begin{fullwidth}
		\begin{centering}
			\includegraphics[width=1.0\linewidth]{figures/supp_figure6.pdf}
			% Need at least one blank line for centering to work.
		\end{centering}
		\caption{
			\label{fig:sup-figure-6}
	{\bf Each replicate of the CDK2/ERK2 calculations yields a consistent RMSE and MUE} \\
	hree replicates of the CDK2/ERK2 calculations with different random seeds, but otherwise the same input structures, files, and parameters. The experimental values are shown on the X-axis and calculated values on the Y-axis. Each data point corresponds to a ligand for a given target. All values are shown in units of kcal/mol. The horizontal error bars show the assumed experimental uncertainty of 0.3 kcal/mol\citep{BROWN2009420}.We show the 95\% CI based on the estimated statistical as vertical blue error bars. For selectivity, the errors were propagated under the assumption that they were completely uncorrelated.  The black line indicates agreement between calculation and experiment, while the gray shaded region represent 1.36 kcal/mol (or 1 log unit) error. The MUE and RMSE are shown on each plot with bootstrapped 95$\%$ confidence intervals. ({\bf A}) Replicate 1 ({\bf B}) Replicate 2 ({\bf C}) Replicate 3}
	\end{fullwidth}
\end{figure}

\begin{figure}[h]
	\begin{fullwidth}
		\begin{centering}
			\includegraphics[width=1.0\linewidth]{figures/supp_figure7.pdf}
			% Need at least one blank line for centering to work.
		\end{centering}
		\caption{
			\label{fig:sup-figure-7}
			{\bf Each replicate of the CDK2/ERK2 calculations yields consistent errors and correlation coefficient} \\
			({\bf A}) (\emph{left}) The joint posterior distribution of the prediction errors for CDK2 (X-axis) and ERK2 (Y-axis) from the Bayesian graphical model for replicate 1. (\emph{right}) The posterior marginal distribution of the correlation coefficient ($\rho$) is shown in gray for replcicate 1. The inserted box shows the mean and 95\% confidence interval for the correlation coefficient. ({\bf B}) and ({\bf C}) The same as above, but for replicates 2 and 3, respectively
		}
	\end{fullwidth}
\end{figure}

\begin{figure}[h]
	\begin{fullwidth}
		\begin{centering}
			\includegraphics[width=1.0\linewidth]{figures/supp_figure8.pdf}
			% Need at least one blank line for centering to work.
		\end{centering}
		\caption{
			\label{fig:sup-figure-8}
			{\bf The pooled replicates show good agreement in predictions for individual ligands} \\
			The experimental values are shown on the X-axis and calculated values on the Y-axis. Each data point corresponds to a ligand for a given target. All values are shown in units of kcal/mol. The horizontal error bars show the assumed experimental uncertainty of 0.3 kcal/mol\citep{BROWN2009420}.We show the 95\% CI based on the estimated statistical as vertical blue error bars. For selectivity, the errors were propagated under the assumption that they were completely uncorrelated. The black line indicates agreement between calculation and experiment, while the gray shaded region represent 1.36 kcal/mol (or 1 log unit) error. The MUE and RMSE are shown on each plot with bootstrapped 95$\%$ confidence intervals. ({\bf Top}) CDK2/CDK9 replicates ({\bf Bottom}) CDK2/ERK2 replicates
		}
	\end{fullwidth}
\end{figure}

\begin{figure}[h]
	\begin{fullwidth}
		\begin{centering}
			\includegraphics[width=1.0\linewidth]{figures/supp_figure9.pdf}
			% Need at least one blank line for centering to work.
		\end{centering}
		\caption{
			\label{fig:sup-figure-9}
		{\bf The standard deviation for each edge is smaller than the estimated cycle closure uncertainties} \\
		The cycle closure uncertainty for each edge of the map is shown on the Y-axis and the standard deviation for that edge in all three replicate calculations is shown on the X-axis, in kcal/mol. Each point corresponds to an edge of the FEP map. The edges for all three replicates are pooled and shown together.  ({\bf Top}) CDK2/CDK9 calculations ({\bf Bottom}) CDK2/ERK2 calculations. 
}
	\end{fullwidth}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
